---
title: "stock-project"
author: "Ziyi Bai"
date: "12/13/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(bizdays)
library(tidyquant)
library(quantmod)
```

### 1. Introduction 

The COVID-19 pandemic has had a devastating effect on the economy in the United States. In early March 2020, the first lockdown began and the stock market plunged. After this initial reaction, however, the market recovered.   

I have discovered the online investment advices from Financial Advisor Magazine published on June 2020. Also, I picked three stocks as combination to simulate invest actions. The first one named GuiZhouMaoTai(600519), which is the most valuable wine company in China. Collecting MaoTai is a symbel of celebrity in China, so I choose this stock in my investment collabpration. BaiDu and Micorsoft  

So, my stock combination is GZMT, BIDU and MSFT based on stock data from 2020-07-01 to 2020-12-02.

### 2. Stock Data
### 2.1 Get Stock Data
```{r,fig.height=3.8}
# get stock data
symbol <- c("MSFT","BIDU","NTES")
dt <- symbol %>% 
  tq_get(get="stock.prices",from = "2020-07-01", to = "2020-12-01")
```

### 2.2 Explore The Data Infomation
### 2.2.1 Initial Exploration
```{r message=FALSE, warning=FALSE}
# Summary of Stock Price
sum_price <- dt %>% 
  select(symbol,date,close) %>% 
  group_by(symbol) %>% 
  summarise(`Min Closing Price` = min(close),
            `Max Closing Price` = max(close),
            `Average Closing Price` = mean(close))

knitr::kable(sum_price,format = "latex",booktabs=T,digits = 2)
```

### 2.2.2. Further Exploration 
```{r}
# Price Trend For Each Stock
dt %>%
    ggplot(aes(x = date, y = adjusted, color = symbol)) + 
    geom_line() +
    facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
    theme_tq() +
    scale_color_tq() +
    labs(title = "Visualize Financial Data")
```

```{r}
# Calculate Monthly Return Rate
stock_returns_monthly <- dt %>% 
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "monthly.return")

stock_returns_monthly %>% 
  ggplot(aes(x = date, y = monthly.return, color = symbol)) + 
    geom_line() +
    theme_tq() +
    scale_color_tq() +
    labs(title = "Movement of Monthly Return Rate",
         subtitle = "From J2020-07-01 to 2020-12-01",
         x = "Date",y="Monthly Return Rate")
```

