---
title: "stock-project"
author: "Ziyi Bai"
date: "12/13/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(bizdays)
library(tidyquant)
library(quantmod)
library(dplyr)
```

### 1. Introduction 

The COVID-19 pandemic has had a devastating effect on the economy in the United States. In early March 2020, the first lockdown began and the stock market plunged. After this initial reaction, however, the market recovered.   

I have discovered the online investment advices from Financial Advisor Magazine published on June 2020. Also, I picked three stocks as combination to simulate invest actions. The first one named GuiZhouMaoTai(600519), which is the most valuable wine company in China. Collecting MaoTai is a symbel of celebrity in China, so I choose this stock in my investment collabpration. BaiDu and Micorsoft  

So, my stock combination is GZMT, BIDU and MSFT based on stock data from 2020-07-01 to 2020-12-02.

### 2. Stock Data
### 2.1 Get Stock Data
```{r,fig.height=3.8}
# get stock data
symbol <- c("MSFT","BIDU","NTES")
dt <- symbol %>% 
  tq_get(get="stock.prices",from = "2020-07-01", to = "2020-12-01")
```

### 2.2 Explore The Data Infomation
### 2.2.1 Initial Exploration
```{r message=FALSE, warning=FALSE}
# Summary of Stock Price
sum_price <- dt %>% 
  select(symbol,date,close) %>% 
  group_by(symbol) %>% 
  summarise(`Min Closing Price` = min(close),
            `Max Closing Price` = max(close),
            `Average Closing Price` = mean(close))

knitr::kable(sum_price,format = "latex",booktabs=T,digits = 2)
```

### 2.2.2. Further Exploration 
```{r}
# Price Trend For Each Stock
dt %>%
    ggplot(aes(x = date, y = adjusted, color = symbol)) + 
    geom_line() +
    facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
    theme_tq() +
    scale_color_tq() +
    labs(title = "Visualize Financial Data")
```

```{r}
# Calculate Monthly Return Rate
stock_returns_monthly <- dt %>% 
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "monthly.return")

stock_returns_monthly %>% 
  ggplot(aes(x = date, y = monthly.return, color = symbol)) + 
    geom_line() +
    theme_tq() +
    scale_color_tq() +
    labs(title = "Movement of Monthly Return Rate",
         subtitle = "From J2020-07-01 to 2020-12-01",
         x = "Date",y="Monthly Return Rate")
```

### 3. Investment Plan
### 3.1 Make some combinations
```{r}
# try another invest rate combination: 30% MSFT, 40% BIDU, 30% NTES
initial_position <- 250000 
wts <- c(0.3,0.4,0.3)
portfolio_growth_monthly_3 <- stock_returns_monthly %>%
    tq_portfolio(assets_col   = symbol, 
                 returns_col  = monthly.return, 
                 weights      = wts, 
                 col_rename   = "investment.growth",
                 wealth.index = TRUE) %>%
    mutate(investment.growth = investment.growth * initial_position)

portfolio_growth_monthly_3 %>%
    ggplot(aes(x = date, y = investment.growth)) +
    geom_line(size = 2, color = palette_light()[[5]]) +
    labs(title = "Portfolio Performance 1",
         subtitle = "30% MSFT,40% BIDU,30% NTES",
         x = "", y = "Portfolio Value") +
    geom_smooth(method = "loess") +
    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar)
```


```{r}
# calculate investment result
initial_position <- 250000 
wts <- c(0.2,0.7,0.1)
portfolio_growth_monthly_1 <- stock_returns_monthly %>%
    tq_portfolio(assets_col   = symbol, 
                 returns_col  = monthly.return, 
                 weights      = wts, 
                 col_rename   = "investment.growth",
                 wealth.index = TRUE) %>%
    mutate(investment.growth = investment.growth * initial_position)

portfolio_growth_monthly_1 %>%
    ggplot(aes(x = date, y = investment.growth)) +
    geom_line(size = 2, color = palette_light()[[5]]) +
    labs(title = "Portfolio Performance 2",
         subtitle = "20% MSFT,70% BIDU,10% NTES",
         x = "", y = "Portfolio Value") +
    geom_smooth(method = "loess") +
    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar)
```
```{r}
# try another invest rate combination: 10% MSFT, 80% BIDU, 10% NTES
initial_position <- 250000 
wts <- c(0.1,0.8,0.1)
portfolio_growth_monthly_2 <- stock_returns_monthly %>%
    tq_portfolio(assets_col   = symbol, 
                 returns_col  = monthly.return, 
                 weights      = wts, 
                 col_rename   = "investment.growth",
                 wealth.index = TRUE) %>%
    mutate(investment.growth = investment.growth * initial_position)

portfolio_growth_monthly_2 %>%
    ggplot(aes(x = date, y = investment.growth)) +
    geom_line(size = 2, color = palette_light()[[5]]) +
    labs(title = "Portfolio Performance 3",
         subtitle = "10% MSFT,80% BIDU,10% NTES",
         x = "", y = "Portfolio Value") +
    geom_smooth(method = "loess") +
    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar)
```

```{r}
# save data for shiny app
write.csv(dt,"dt.csv")
```


### 3.2 Check stock performance
```{r}
Ra <- c("MSFT", "BIDU", "NTES") %>%
    tq_get(get  = "stock.prices",
           from = "2020-07-01",
           to   = "2020-12-01") %>%
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Ra")
Ra
```
```{r}
# get baseline
Rb <- "IVE" %>%
    tq_get(get  = "stock.prices",
           from = "2020-07-01",
           to   = "2020-12-01") %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Rb")
Rb
```
```{r}
# combine the dataset
RaRb <- left_join(Ra, Rb, by = c("date" = "date"))
RaRb
```
```{r}
RaRb_capm <- RaRb %>%
    tq_performance(Ra = Ra, 
                   Rb = Rb, 
                   performance_fun = table.CAPM)
RaRb_capm %>% select(symbol, Alpha, Beta)
```


